%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% abstract.tex: Abstract This is the Abstract Section of Analysis.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Dark matter particles are believed to be neutral, stable, weakly interacting with ordinary matter and maybe massive. The hunt for dark matter particles is on! There are theoretical models which predict the  existence of dark matter particles that can be produced in a proton-proton collider like the Large Hadron Collider provided there is sufficient center of mass energy. Gauge Mediating Supersymmetric Models are examples of such models. These models describe the production and decay into isolated energetic photons, new, massive, neutral, weakly interacting particles known as supersymmetric particles. The Neutralino~($\tilde{\chi}^{0}_{1}$), being the lightest supersymmetric particle in terms of mass, is a prime example and its decay into a photon is accompanied by a light weakly interacting and stable supersymmetric particle, the gravitino~($\tilde{G}$) which is considered to be a very good candidate for dark matter particles. The resulting photon from such a decay, is understood to be delayed in its arrival time at the detector. This timing delay is due to inherent dynamics understood and well described by models beyond the standard model. The signature of a delayed photon is not specific to only supersymmetric models but could be the result of probably some new kind of physics unrelated to the standard model. Using the Compact Muon Solenoid detector at the LHC, we have performed a search for delayed photons produced from proton-proton collisions at the center of mass energy, $\sqrt{S} = 8$~TeV. We did not find any excess of events over standard model background. Consequently, we compute an upper limit on the cross section $\sigma_{\tilde{\chi}^{0}_{1}} > 0.02$~pb of the production and decay of the lightest neutralino with  mass and proper lifetime; $m_{\tilde{\chi}^{0}_{1}} \geq 235$~\GeVcc and $\tau_{\tilde{\chi}^{0}_{1}} \ge 35$~ns respectively, as described in a minimal gauge mediated supersymmetric model. We also show that using only the timing information of the electromagnetic calorimeter as observable, the  CMS detector is sensitive to neutralinos with lifetimes up to $30$~ns and mass, $m_{\tilde{\chi}^{0}_{1}} \approx 260$\GeVcc which no previous experiment could show. We provide possible improvements  of our search analysis which might help discover delayed photons in future.