%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% acknowledge.tex: Acknowledgements
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%\textbf{ My younger brother, Adolf Bessem Dikonge, died on the 26th July, 2015 at the age of 24 years.
%%For some reason, I have no idea where I am pulling the strength to carry on with writing and editing this thesis while at the same time making arrangements for his burial on the 22nd of August, 2015. How in the world am I pulling this off? }
I want to begin by thanking all the students and postdocs in the High Energy Physics research groups: Theory, CMS, Neutrino and CDMS for their kind discussions and continuous help and to the people I shared office and collaborated with during my time at CERN. I thank Dr. Shih-Chuan Kao for the lively discussions, technical help and for working tirelessly to get this analysis approved for publication. A lot of things would have taken a lot more time without his timely intervention.
I thank Professors Jeremiah Mans and Roger Rusack for their patience and for providing me with all the help I needed to be able to do experimental High Energy Physics.
\newline
I thank my adviser  Prof. Yuichi Kubota first of all for accepting to be my adviser, a unique opportunity at a time when my flaws as an experimental High Energy Physicists were numerous. He gave me numerous opportunities to experience failure and improvement and his unbelievable patience with my stubborn ignorance still amazes me. Thank you, I could not have had a better adviser. Through all his efforts, I have not only become a better Physicists but also a better human being.
\newline
I thank my wonderful wife Mary Sylvia for her patience and selflessness, while also a graduate student in Mathematics she always found the time to chat or listen as I mourn endlessly about my struggles doing research and for the wonderful gift of our son Neilton who continuously gives me joy especially during those very stressful periods in this journey. I recall taking him to the play ground and watch him play with freedom and joy. Neilton, you are an absolute joy and blessing to us.
I thank my parents for their continuous support, patience and endless prayers. 
\newline
I thank the Graduate School of University of Minnesota for awarding me the Doctoral Dissertation Fellowship in 2013/2014 which supported this study. \newline
Finally I thank God almighty without whom all this would not have been possible.



\begin{comment}
Humility is not about thinking less of yourself, rather, humility is thinking about yourself less.
There are many people that have earned my gratitude for their contribution to my
time in graduate school. 
%%I want to thank my supervisor Prof. Yuichi Kubota, who gave me countless failure-tolerant opportunities
%%throughout my PhD. Before I knew him, the fear of failure always did paralyzed me, not anymore.
%%\textit{The universe is unbiased, she chooses to reveal herself to all who have the \textit{right} attitude.}
%%\newline
%%\textsf{Tambe E. Norbert}
%%\newline
\textit{So I would claim you are profoundly misled by thinking about physics as similar to logic or number theory. It’s not! it’s dynamical evolution, and most results of physics problems are not nice numbers like 1 or $\pi$ or even $e^{\pi}$.}
\newline
\textsf{Matt Strassler}
\par 
\textit{The Universe is unbiased, she chooses to reveal herself to whoever she wants, irrespective of the label.}
\newline
Norbert E. Tambe

\end{comment}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
