%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Understanding the multiverse will always be my dream. According to my parents, it began in my infant years. However, in the later years of my life I kept feeling I really did not have the aptitude to understand even the universe we currently live in and I really did not have the favor of the universe  to pursue such a dream. The aptitude part changed when I was taught physics in high school by an American Peace Corp call Mr. Jeff and the favor part changed when I finally learned how to interpret unfortunate circumstances like the death of my younger sibling Dikongue Bessem Adolf at about 9:00am on Sunday, July 26th 2015 at my parent's home in Bonadikombo, Limbe. I still believe Adolf is here!
\par
I dedicate this thesis to Mr. Jeff who taught me Physics in a really really simple and unbelievably "sticky" way. The concepts of physics I learned from him stuck with me forever. 
I also dedicate this thesis to my younger brother Adolf Bessem Dikongue, who was always very understanding and very patient and to late Professor Mohammad Abdus Salam~(Nobel Prize Physics 1979), his vision of the ICTP has enabled \textit{Les Mis$\acute{e}$rables} like myself to continuously dream of understanding the complexity of the universe.
Finally, I dedicate this thesis to all those who continuously feel they don't belong and don't have what it takes to feel belonging and excel in their dream. Know this, it is really simply a matter of time, hang in there, you will eventually belong.
\begin{comment}
\par 
\textsf{“What ever it is that doesn\textquotesingle t workout, get up...I think you\textquotesingle ve got to realized that there is no personal ambition you have which can be extinguished by anybody else...Only YOU by giving up your dreams can extinguish them. And if your dreams doesn't work out EXACTLY like you intended, it will still take you someplace interesting and you will make a DIFFERENCE. So, DON\textquotesingle T be AFRAID TO FAIL because you probably will whether you are afraid to or not and it's scary. You just gotta get out. 
The world belongs to tomorrow not yesterday. Don\textquotesingle t give anybody else permission to take your life away, just keep living and keep giving and never make the perfect enemy the good. Never think that what I\textquotesingle m doing is too little to make a difference, THAT\textquotesingle S NOT TRUE!, THAT\textquotesingle S NOT TRUE!  Do something everyday. Someday, for all of us, it will be our last day and what would matter will be all the steps we took along the way and what they amounted to, NOT the home run we hit on day X. I wish you well.”}
\newline
\texttt{US Pres  Bill Clinton, Dallas, TX}
\par
\par 

\textit{No, I have nothing against Mr. Einstein. He is a kind person and has done many good things, some of which will become part of the music. I will write to him and try to explain that the ether exists, and that its particles are what keep the Universe in harmony, and the life in eternity}. 
\newline
Nikola Tesla
\end{comment}
