\begin{thebibliography}{9}
%%% DARK MATTER/MOTIVATIONS
\bibitem{DM} N. Jarosik et al. (WMAP), Astrophys. J. SUppl. \textbf{192}, 14 (2011); Overview: K.A. Olive et al.(PDG), Chin.Phys.C\textbf{38},090001(2014).
\bibitem{SUSYDM} Ellis John, Olive Keith A. (2010). \textit{Supersymmetric Dark Matter Candidates}. arXiv:1001.3651 [astro-ph]
\bibitem{LSPDM} Laura Covi, \textit{Gravitino Dark Matter confronts LHC} Journal of Physics: Conference Series 485 (2014) 012002
\bibitem{DMS} M. Kuhlen, M Vogelsberger, R. Angulo, Phys.Dark Univ.\textbf{1},50(2012).
\bibitem{KOlive} J.Ellis, J.Hagelin, D. Nanopoulos, K.A. Olive and M. Srednicki; \emph{Nucl. Phys.} B238~(1984) 453; H. Goldberg, \emph{Phys. Rev. Lett} 50~(1983) 1419;
J. Ellis, T. Falk, G. Ganis, K.A. Olive and M. Srednicki, \emph{Phys. Lett.} B 510~(2001) 236, arXiv: hep-ph/0102098.
\bibitem{SMREV} K.A. Olive et al. (Particle Data Group), Chin. Phys. C, 38, 090001 (2014).
\bibitem{SWG}  Steven Weinberg, \textit{A Model of Leptons}, \emph{Phys. Rev. Lett.} 19, 1264–1266 (1967)
\bibitem{HIGGS} Peter W. Higgs \textit{Broken symmetries and the masses of gauge bosons}, \emph{Phys.Rev.Lett.13.508},19 October, 1964;
\bibitem{HIGGSD}\textit{Observation of a new boson at a mass of 125~GeV with the CMS experiment at LHC}, \emph{Phys. Lett. B 716~(2012) 30-61}

%\bibitem{Quarks} "Observation of a Charged Charmoniumlike Structure in $\Pelectron\Ppositron \rightarrow \Ppiplus\Ppiminus\PJpsi$ at $ \sqrt{S} = 4.26$  GeV" M. Ablikim et al. \emph{Phys. Rev. Lett.} 110, 252001 (2013), "Study of $\Pelectron\Ppositron \rightarrow \Ppiplus\Ppiminus\PJpsi$ and Observation of a Charged Charmoniumlike State at Belle", Z. Q. Liu et al. \emph{Phys. Rev. Lett.} 110, 252002 (2013);


%\bibitem{g2ex}H. N. Brown et al., Muon $g_{\mu}-2$ Collaboration, \emph{Phys. Rev. Lett} 88~(2002) 2227, hep-ex/0102017; A. Czarnecki and W.J. Marciano,\emph{ Phys. Rev.} D 64~(2001) 013014, hep-ph/0102122.
%\bibitem{g2Theory} M. Knecht and A. Nyffeler, hep-ph/0111058; I. Blokland, A. Czarnecki and K. Melnikov \emph{Phys.Rev. Lett} 88~(2002) 071803 hep-ph/0112117
%\bibitem{BSex}CLEO Collaboration, M. S Alan et al., \emph{Phys. Rev. Lett.} 74~(1995) 2885 as updated in S. Amed et al., CLEO CONF 99-10; 
%\bibitem{BELL} BELLE Collaboration hep-ex/0103042;

%%% Theory of SUSY/GMSB
\bibitem{MSUSY} Haag, Rudolf; Sohnius, Martin; Łopuszański, Jan T. \textit{All possible generators of supersymmetries of the S-matrix}, Nuclear Physics B 88: 257–274 (1975),
\bibitem{SALAM} Salam, A.; Strathdee, J. (1974). \textit{Super-gauge transformations}. Nuclear Physics B 76 (3): 477–201,
\bibitem{MSSM} Ian J R Aitchison, \textit{Supersymmetry and the MSSM: An Elementary Introduction}, arXiv:hep-ph/0505105,
\bibitem{SUSYM} S.Mathin,\textit{Supersymmetry Primer}, arXiv:hep-ph/9709356,
\bibitem{SUSYBOOK} Howard Baer, Xerxes Tata, \textit{Weak Scale Supersymmetry:From Superfields to Scattering Events}.
\bibitem{SUSYN} H. Nilles, \textit{Supersymmetry, Supergravity and Particle Physics}, Phys. Rept. 110(1984) 1.
\bibitem{GMSB}G.F. Giudice and R. Rattazzi \textit{Theories with Gauge-Mediated Supersymmetry Breaking} arXiv:hep-ph/9801271v2.
\bibitem{NLSP} S. Ambrosanio 1 , Graham D. Kribs 2 , and Stephen P. Martin hep-ph/9703211 arXiv:hep-ph/9703211v2.
\bibitem{SPS8} B.Allanach et al,arXiv:hep-ph/0202233v1.

\bibitem{Algo} D.del Re et al, \textit{An algorithm for the determination of the flight path of long-lived particles decaying into photons}, CMS AN -2010/212.

%%%% Event Generation & Simulation
\bibitem{ISAJET} ISAJET 7.84, F.E. Paige, S.D. Protopopescu, H. Baer and X. Tata, http://www.nhn.ou.edu/~isajet/
\bibitem{PYTHIA6} T. Sj ostrand, S. Mrenna, and P. Skands, \textit{PYTHIA 6.4 physics and manual}, JHEP 05 (2006) 026, doi:10.1088/1126-6708/2006/05/026, arXiv:hep-ph/0603175
\bibitem{GEANT4} GEANT4 Collaboration, \textit{GEANT4—a simulation toolkit}, Nucl. Instrum. Meth. A 506(2003) 250, doi:10.1016/S0168-9002(03)01368-8.


%%%% Previous Experiments
\bibitem{LEP}J.Dann et al.(LEPSUSY Working Group), Internal note LEPSUSYWG/97-04(1997), P. Janot, talk at the EPS Conference, Jerusalem, 1997.
\bibitem{CDF}CDF Collaboration, \textit{Search for Supersymmetry with Gauge-Mediated Breaking in Diphoton Events with Missing Transverse Energy at} CDFII,\emph{Phys. Rev. Lett.}
\bibitem{ATLAS} ATLAS Collaboration \textit{Search for Diphoton Events with Large Missing Transverse Momentum in \text{1 $fb^{-1}$} of $\text{7TeV}$ Proton-Proton Collision Data with the ATLAS Detector}, arXiv:1111.4116v1,17th Nov 2011. 
\bibitem{CMS}CMS Draft Analysis,\textit{Search for Long-Lived Particles using Displaced Photons in \emph{PP} Collision at $\sqrt{S}=7\TeV$}, CMS AN AN-11-081 \emph{$104(2010) 011801,$}
\bibitem{ATLAS1}ATLAS Collaboration, J. High Energy Phys. 1212, 124
(2012), arXiv:1210.4457 [hep-ex]

%%% LHC & CMS EXPERIMENTS
\bibitem{LHC} The LHC Machine, Lyndon Evans and Philip Bryant \textit{Jinst},
\bibitem{CMSTDR}CMS Collaboration,\textit{CMS Physics: Technical design report}, Volume 1 CERN-LHCC-2006-001.
\bibitem{TDR}CMS Collaboration,\textit{CMS Physics: Technical design report, Volume 2} CERN-LHCC-2006-001.
\bibitem{LHCB} The CERN Brochure 2009-003-Eng.
\bibitem{JINST}CMS Collaboration, \textit{The CMS experiment at the CERN LHC}, JINST 0803:S08004, 2008.
\bibitem{cmsdata}CMS Collaboration, \textit{CMS trigger and data taking in 2010},\emph{CMS CR-2011/051}.

%%%% TIMING: LHC/CMS
\bibitem{LHCT} \textit{Timing Distribution at the LHC},  B.G. Taylor Colmar, 9-13 September 2002
\bibitem{LHCT1} \textit{An FPGA based multiprocessing CPU for Beam
Synchronous Timing in CERN’s SPS and LHC}.\emph{Proceedings of ICALEPCS2003, Gyeongju, Korea
ICALEPCS 2003}
\bibitem{LHCT2} \textit{Timing and Synchronization in the LHC Experiments}, Varela, J. Krakóv, 11-15 September 2000.
\bibitem{LHCT3} http://ttc.web.cern.ch/TTC/intro.html
\bibitem{ATLAS-GHOST} \textit{Study of the LHC ghost charge and
satellite bunches for luminosity calibration.}, CERN-ATS-Note-2012-029 PERF
\bibitem{CMS-GHOST} \textit{LHC bunch current normalization for the April-May 2010 luminosity calibration measurements.}, CERN-ATS-Note-2011-004 PERF

%% ECAL TIMING CALIBRATION
\bibitem{ECALTDR}CMS Collaboration,\textit{The electromagnetic calorimeter. Technical design report},. CERN-LHCC-97-33.
\bibitem{ECALREADOUT} Bo Lofstedt, \textit{The digital readout system for the CMS electromagnetic Calorimeter},\textit{Nucl. Inst.  Methods in Physics Research},A 453~(2000) 433-439.
\bibitem{ECAL}CMS Electromagnetic Calorimeter Collaboration, \textit{Energy resolution of the barrel of the CMS Electromagnetic Calorimeter},JINST 2(2007)P04004.
%% ECAL TIMING
\bibitem{RECOAMPLI}CMS Collaboration, \textit{Reconstruction of the signal amplitude of the CMS electromagnetic Calorimeter}, Eur.Phys.J. C46S1(2006)23-35.
\bibitem{TIME}CMS Collaboration, \textit{Time Reconstruction and Performance of the CMS Crystal Electromagnetic Calorimeter},CFT-09-006, 2009.
\bibitem{ECALCAL} https://twiki.cern.ch/twiki/bin/viewauth/CMS/ECALDPGTimeCalibration
\bibitem{ECALHW}https://twiki.cern.ch/twiki/bin/viewauth/CMS/ECALDPGHwTimeCalibration
\bibitem{ECALTIME}CMS Collaboration, \textit{The CMS ECAL performance With examples}, JINST 9 C02008, 2014.
\bibitem{ECALTD} Daniele Del Re for CMS Collaboration, \textit{Timing performance of the CMS electromagnetic calorimeter and prospects for the future.}, CMS-CR-2014/074
\bibitem{ECALTIME2014} CMS-DP-2014/011: \textit{ECAL Timing Performance Run1}
\bibitem{ECALT} https://twiki.cern.ch/twiki/bin/view/CMSPublic/EcalDPGResultsCMSDP2014011
\bibitem{ECALTIMEUPGRADE}https://twiki.cern.ch/twiki/bin/view/CMSPublic/EcalDPGResultsCMSDP2014012

%%%% PHYSICS OBJECT RECO
\bibitem{PFALGO} Florian Beaudette (the CMS Collaboration), \textit{The CMS Particle Flow Algorithm}, arXiv:1401.8155 [hep-ex]. 
\bibitem{PF}CMS Collaboration, \textit{Particle-Flow Event Reconstruction in CMS and Performance for Jets, taus and \ETslash}, CMS Physics Analysis Summary \boldmath{CMS-PAS-PFT-09-001}(2009).
\bibitem{JET} CMS Collaboration, \textit{Jet Performance in pp Collisions at $\sqrt{S} = 7\TeV$},
CMS PAS JME-10-003 (2010).
\bibitem{JEC}  CMS Collaboration, \textit{8 TeV Jet Energy Corrections and Uncertainties based on 19.8 \fbinv of data in CMS}, CMS-DP-2013-033 ; CERN-CMS-DP-2013-033, \textit{Jet Energy Corrections and Uncertainties}, CMS Public Note CMS-DP-2012/012.
\bibitem{MET2}CMS Collaboration, \textit{Missing Transverse Energy Performance in Minimum-Bias and Jet Events from Proton-Proton Collisions at $\sqrt{s} =7$\TeV}, CMS Physics Analysis Summary CMS-PAS-JME-10-004 (2010).
\bibitem{MET}CMS Collaboration, \textit{Missing transverse energy performance of the CMS detector}, arXiv:1106.5048v1., Missing Transverse Energy, JINST ,arXiv:1106.5048.

%SPIKES DOCS
\bibitem{spike} \textit{Characterization and treatment of anomalous signals in the CMS Electromagnetic Calorimeter} CMS AN AN-10-357.
\bibitem{spike2} \textit{Mitigation of Anomalous APD signals in the CMS ECAL},\textit{2013, JINST 8 C03020}, W.Bialas and D.A. Petyt.


\bibitem{JES} CMS Collaboration,\textit{Determination of Jet Energy Scale in CMS with pp collisions at $\sqrt{S} = 8$\TeV}, JME-10-010(2012).
\bibitem{PES} "https://twiki.cern.ch/twiki/bin/viewauth/CMS/EGamma2012."
\bibitem{METRES} CMS Collaboration, \textit{Search for ADD Extra-dimensions with Photon + MET signature}, AN-11-319(2011).
\bibitem{PDF} \textit{Parton distributions for the LHC}, Eur.Phys.J C63(2009) 189-285 or arXiv:0901.0002.


%%% Limits & Results
\bibitem{CLS} \textit{Presentation of search results: the CLs technique},A L Read 2002 J. Phys. G: Nucl. Part. Phys. 28 2693.
\bibitem{LIMITS} \textit{Computation of confidence levels for search experiments with fractional event counting and the treatment of systematic errors}, Peter Bock JHEP01(2007)080.
\bibitem{LIMITS} https://twiki.cern.ch/twiki/bin/viewauth/CMS/
\bibitem{ASYMP}  \textit{Asymptotic formulae for likelihood-based tests of new physics},G. Cowan et al, arXiv:1007.1727v3.

%\bibitem{GDM} N.-E. Bomark and L. Roszkowski "3.5 keV x-ray line from decaying gravitino dark matter" Phys. Rev. D 90, 011701(R) – Published 18 July 2014





%\bibitem{PGGM} Steven Abel a,b , Matthew J. Dolan et al "Pure General Gauge Mediation for Early LHC Searches"  arXiv:1009.1164v2 [hep-ph].

%\bibitem{GGM}M. Dine and A. E. Nelson, Phys. Rev. D 48, 1277(1993), arXiv:hep-ph/9303230

%\bibitem{GGM1}P. Meade, N. Seiberg, and D. Shih, Prog. Theor. Phys. Suppl. 177, 143 (2009), arXiv:0801.3278 [hep-ph]

%\bibitem{GGM2}M. Buican, P. Meade, N. Seiberg, and D. Shih, J. High Energy Phys. 0903, 016 (2009), arXiv:0812.3668 [hep-ph]

%\bibitem{MDINE1}M. Dine, A. E. Nelson, and Y. Shirman, Phys. Rev. D 51, 1362 (1995), arXiv:hep-ph/9408384

%\bibitem{MDINE2}M. Dine, A. E. Nelson, Y. Nir, and Y. Shirman, Phys.Rev. D 53, 2658 (1996), arXiv:hep-ph/9507378
%\bibitem{DSHIH} J. T. Ruderman and D. Shih, J. High Energy Phys.1208, 159 (2012), arXiv:1103.6083[hep-ph]



\end{thebibliography}